---
title: "Lab 1: Introduction to Quarto"
author: "Tillman Erb"
format: 
  html:
    toc: true
editor: source
embed-resources: true
code-fold: true
theme: darkly
execute:
  echo: true
  error: true

---

To do: revise code spacing, revise formatting, make figure caption one instead of two

# Part Two: Exploring Quarto Documents

## 1.0: Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be displayed. This [guide](https://quarto.org/docs/computations/execution-options.html) provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML.

**Question 2** -- Add an `execute` line to your YAML that includes the following options, (1) your source code is always output on the page, and (2) your document will render even if there are errors.

## 2.0: Loading Guinea Pig Orange Juice Dataset

```{r}
#| eval: false
#| echo: true
#| label: practicing-running-code

# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)
```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code chunk and paste in the code provided in the Lab 1 instructions.

### 2.1: Check the Data Documentation

**Question 4** -- In your **console** (*not* in the Quarto document), type `?ToothGrowth` (or alternatively `help(ToothGrowth)`.Use the information that pops up in the *Help* pane in RStudio to fill in the blanks below.

*This dataset investigates the effect of Vitamic C on tooth growth in Guinea Pigs.*

*The two supplement delivery methods include OJ (orange juice) and VC (vitamin C).*

*`ToothGrowth` is a data frame with 60 observations and 3 variables.*

**Question 5** -- *Before* the code chunk, change the "Running the Provided Code" section header to a header that better describes the contents of this section (e.g., Tooth Growth Dataset).

## 3.0: Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-cap: 
#|    - "Box plot of guinea pig tooth growth for doses of OJ and Vitamin C"
#|    - "Tooth growth in guinea pigs by doseage"
#| fig-align: center

library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")
```

Now, run this code chunk! You should see two side-by-side boxplots, one plot comparing tooth length between the two supplement delivery methods and one plot comparing tooth length between the three different dosages uses.

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations) and add an option (`#|`) to the above code chunk to make the figures print side-by-side (i.e., in one row) in the rendered HTML file.

**Question 8** -- Specify in the code chunk options that these boxplots should be **center aligned**.

**Question 9** -- Specify a **figure caption** for the boxplots (using a code-chunk option).

## 4.0: Implmenting and analyzing a two-sample t-test
**Question 10 & Question 11**
```{r}
#| eval: true
#| echo: true
#| label: T test code block

#2-sample t-test on tooth growth between doses of OJ and VC
t.test(len ~ supp, data = ToothGrowth)
```

**Question 12**

1. Conclusion: With a p-value of 0.06 approaching a statistically significant value of p = 0.05, we fail to reject the null hypothesis and conclude that there is not sufficient evidence to prove that there is a statistically significant difference in  mean tooth growth in guinea pigs between doses of orange juice and vitamin C.
2. We are 95% confident that the true difference between orange juice and vitamin C (OJ -  VC) lies in between -0.17 and 7.57.
